Discrete Quantum Theories and Computing

### 2019-04-16 dissertation.tex
dissertation.lyx "6.1 Summary" Updating...

The theories over finite fields starting with unrestricted discrete
fields (modal theories), then advancing to a more reasonable framework
based on complexifiable discrete fields (discrete quantum theory I),
which lacks a notion of probability and supports unnaturally efficient
deterministic quantum algorithms. A still more plausible discrete
theory (discrete quantum theory II) is proposed, where conventional
quantum theory and computing emerge in a local sense. However, since

\todo{Clean up until here\ldots}

>>>>

The theories over finite fields started with unrestricted discrete
fields (Chapter~\ref{chap:Unrestricted-Finite-Fields}), then advanced
to a more reasonable framework based on complexifiable discrete fields
(Sec.~\ref{discretequantumtheoryI} to~\ref{discretequantumcomputingI}),
which lacks a notion of probability and supports unnaturally efficient
deterministic quantum algorithms. A still more plausible discrete
theory with cardinal probabilities is proposed (Sec.~\ref{sec:Discrete-Quantum-Theory-(II)}
and~\ref{discretequantumcomputingII}), where conventional quantum
theory and computing emerge in a local sense, but lacking arithmetic
operations among cardinal probabilities still posed difficulty to
define expectation values. One attempt to address this issue was to
switch to an axiomatic approach and following Gleason's theorem to
deduce a Born rule over finite fields (Sec.~\ref{sec:Toward-IVPM}).
However, quantum theories over finite fields looked unlikely to compatible
with infinitely precise real-valued probability; we thus extended
the classical imprecise interval-valued probability to quantum domain,
and defined quantum interval-valued probability measures (QIVPMs).

\begin{figure}[b]
\centering{}$\xymatrix{\textrm{Classical Probability Measure}\ar[d]\ar[r] & \textrm{Quantum Probability Measure}\ar[d]\\
\textrm{Classical IVPM}\ar[r] & \textrm{QIVPM}
}
$\caption{\label{fig:commutative-diagrams}Quantum IVPMs inherited from both
quantum probability measures and classical IVPMs. Since Quantum IVPMs
inherited from classical probability measures in two different paths,
it is natural to ask whether this diagram commutes.}
\end{figure}
As a natural extension of both convention quantum probability measures
and classical interval-valued probability measures (IVPMs) illustrated
in Fig.~\ref{fig:commutative-diagrams}, QIVPMs inherited definitions
and properties from the both sides. While the core and expectation
values of QIVPMs can be pulled back to the classical cases and consistent
with those of quantum probability measures in the infinitely precise
limit (Sec.~\ref{sec:Interval-Uncertainty}), foundational concepts
in quantum mechanics, such as the Kochen-Specker and Gleason theorems,
extended to QIVPMs in subtle ways. \todo{Clean up until here\ldots}

Similar to gluing a family of classical probability spaces together
to form a conventional quantum probability space (Sec.~\ref{sec:fuzzy}),
a family of classical IVPMs can be glued to get a quantum IVPM. Although
most of structures above classical IVPMs can be extended to the quantum
case (Sec.~\ref{sec:Interval-Uncertainty}), .
